---
title: "Cod_Ex"
author: "Kate Bakova"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE) 
```

```{r}
source("setup.R")
```

```{r}
data("knz_bison")
```

#1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.

```{r}
knz_bison <- knz_bison%>%
mutate(age = knz_bison$rec_year - knz_bison$animal_yob)
```

#2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
bison_weight <- function(weight) {
 knz_bison %>% 
  filter(knz_bison$animal_weight >= weight)
 }
bison_weight(1000)
```


#3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
ggplot(data = knz_bison) +
  geom_boxplot(mapping = aes(x = animal_sex, y = animal_weight))
```

```{r}
 knz_bison %>% 
t_test(animal_weight ~ animal_sex, var.equal = FALSE, detailed = TRUE) 
```

p<0.05, so there is significantly difference between males and females weight.



